PANCHANGE_data_preprocessing

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd

# Specify cohort
```{r Specify cohort}
GLAD = FALSE
EDGI = FALSE
NBR = FALSE
RAMP = TRUE
```

@@

dat.coping <- left_join(
  x = dat,
  y = respiratory,
  by = "ID"
)
```

>>>>

# Specify cohort
```{r Specify cohort}
GLAD = TRUE
EDGI = FALSE
NBR = FALSE
RAMP = FALSE
```

@@

dat.coping <- left_join(
  x = dat,
  y = respiratory,
  by = c("Sample", "ID")
)
```
